---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Lab Report

### Step 1 Result

```{r}
library(classdata)

head(ames, 5)
summary(ames)
str(ames)
```

Variables:

1. Parcel ID (chr) - An unique ID
2. Address (chr) - Address of residence
3. Style (Factor) - Number of stories
4. Occupancy (Factor) - Type of residence
5. Sale Date (Date) - Date of sale
6. Sale Price (num) - Sale price
7. Multi Sale (chr) - Multiple sales
8. YearBuilt (num) - The year it was built
9. Acres (num) - Acres of the residence
10. TotalLivingArea (sf) (num) - Total living area of residence
11. Bedrooms (num) - Number of bedrooms
12. FinishedBsmtArea (sf) (num) - Basement area
13. LotArea (sf) (num) - Lot area
14. AC (chr) - Availability of AC
15. FirePlace (chr) - Availability of fire place
16. Neighborhood (Factor) - Neighborhood it belong in

Variables with chr type have no restriction in data range, could be any string or they could be categorical data.

Variables with Date type has a format of year-month-date

Variables with num type have an infinite data range of any number

Varibles with Factor type have categorical data stored on different levels of a data structure but no restriction on number of levels

### Step 2 Result

### Step 3 Result

### Step 4 Result
