---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Lab Report

### Step 1 Result

```{r}
library(classdata)
library(tidyverse)
library(ggplot2)

head(ames, 5)
summary(ames)
str(ames)
```

Variables:

1. Parcel ID (chr) - An unique ID
2. Address (chr) - Address of property
3. Style (Factor) - Number of stories
4. Occupancy (Factor) - Type of property
5. Sale Date (Date) - Date of sale
6. Sale Price (num) - Sale price
7. Multi Sale (chr) - Multiple sales
8. YearBuilt (num) - The year it was built
9. Acres (num) - Acres of the property
10. TotalLivingArea (sf) (num) - Total living area of property
11. Bedrooms (num) - Number of bedrooms
12. FinishedBsmtArea (sf) (num) - Basement area
13. LotArea (sf) (num) - Lot area
14. AC (chr) - Availability of AC
15. FirePlace (chr) - Availability of fire place
16. Neighborhood (Factor) - Neighborhood it belong in

Variables with chr type have no restriction in data range, could be any string or they could be categorical data.

Variables with Date type has a format of year-month-date

Variables with num type have an infinite data range of any number

Varibles with Factor type have categorical data stored on different levels of a data structure but no restriction on number of levels

### Step 2 Result
The variable of special interest is Sale Price. When exploring various relationships with other variables, Sale Price seems to result in the most correlation. Living Area, Year Built, and Neighborhood seem to have some correlation with Sale Price.



### Step 3 Result
```{r, message=FALSE}

library(classdata)
library(ggplot2)

#summary(ames)

#ames$`Sale Price`

hist <- ggplot(ames, aes(x=log(`Sale Price`))) + geom_histogram(binwidth=.1) + ggtitle("Histogram for Sale Price of Residential Sales in Ames")  + labs(x="Sale Price")
hist

#range(ames$`Sale Price`)

```

The range of the variable is 0 to 20,500,000 with 0 as the minimum and 20,500,000 as the maximum.

As you can see, the histograms most common values are from about 12-13 on the log scale.
If we wanted to look at the numerical values for Sale Price I would estimate (since our x values are measured in log(Sale Price)) that it would fall between about 162,755 dollars and about 442,413 dollars.

As for oddities, I think it's strange that for some houses the sale price is 0. I also think that there are some very high values as outliers, to the right of the largest part of the histogram, especially considering how many of these outliers there are. 

### Step 4 Result
<<<<<<< HEAD
<<<<<<< HEAD
**Nadia's work**:
  I selected the square feet of living area. Based on the histogram, it appers the data are slightly right-skewed, and that square footage around 1000-1500 is most common. I decided to drop rows with NA values, or those with price or square footage listed as 0, as these were likely errors. After making a scatterplot, I saw that there was only a small positive correlation between price and size, which surprised me. I also noticed that there were a few houses with prices so high that it made the plot difficult to read, so I ran the prices through a log function first.

``` {r}
#Nadia
df <- ames['TotalLivingArea (sf)']
df['Price'] <- ames['Sale Price']
df['SqFtLiving'] <- ames['TotalLivingArea (sf)']
df <- drop_na(df)
df <- filter(df, Price>0, SqFtLiving>0)
ggplot(df, aes(x=SqFtLiving)) +
  geom_histogram(binwidth = 100)
ggplot(df, aes(x=SqFtLiving, y=log(Price))) +
  geom_point()

```
=======
=======
>>>>>>> 5622e974afc9391b83d7b7e0c7a72be67de70931

``` {r}
# df <- df['Price']
# df['Price'] <- ames['Sale Price']
# df['SqFtLiving'] <- ames['TotalLivingArea (sf)']
# df <- drop_na(df)
# head(df)
# ggplot(df, aes(x=SqFtLiving)) +
#   geom_histogram(binwidth = 100)
# ggplot(df, aes(x=SqFtLiving, y=log(Price))) +
#   geom_point()
```

=======
>>>>>>> 5622e974afc9391b83d7b7e0c7a72be67de70931

``` {r}
# df <- df['Price']
# df['Price'] <- ames['Sale Price']
# df['SqFtLiving'] <- ames['TotalLivingArea (sf)']
# df <- drop_na(df)
# head(df)
# ggplot(df, aes(x=SqFtLiving)) +
#   geom_histogram(binwidth = 100)
# ggplot(df, aes(x=SqFtLiving, y=log(Price))) +
#   geom_point()
```

Hong Hao's work:YearBuilt vs Sale Price

  
Hong Hao's work:YearBuilt vs Sale Price  
```{r}
library(ggplot2)

ggplot(data = ames, aes(x = `Sale Price`, y = YearBuilt)) +
<<<<<<< HEAD
<<<<<<< HEAD
#>>>>>>> b990b4fe3c5ce6598d64fdafd73f8d506d935108
=======
>>>>>>> 5622e974afc9391b83d7b7e0c7a72be67de70931
=======
>>>>>>> 5622e974afc9391b83d7b7e0c7a72be67de70931
  geom_point()
```

Kaitlyn's work: Bedrooms
```{r}

# Include at least one plot that describes the relationship between sales prices and your variable. Include one paragraph describing the pattern you see. Are there oddities? Follow-up on (some of) them.
#what is the range of that variable? plot. describe the pattern.
#what is the relationship to the main variable? plot a scatterplot, boxplot or facetted barcharts (dependening on the types of variables involved). Describe overall pattern, does this variable describe any oddities discovered in 3? Identify/follow-up on any oddities.

```
